Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-09-20 paper/main.tex
add future work idea

\begin{itemize}
    \item Highlight methodological advancements
    \item Constructed Model which already combines many effects; extend this even further
    \item can now use classical methods: sensitivity-analysis, likelihood estimators and uncertainty quantification
    \item Proof of concept: Able to fit individual parameters of the agents; can be extend this?
    \item Provide software package which combines all functionality and is readily available
\end{itemize}

>>>>

\begin{itemize}
    \item Highlight methodological advancements
    \item Constructed Model which already combines many effects; extend this even further
    \item can now use classical methods: sensitivity-analysis, likelihood estimators and uncertainty quantification
    \item Proof of concept: Able to fit individual parameters of the agents; can be extend this?
    \item Provide software package which combines all functionality and is readily available
    \item Future work:
    \begin{itemize}
        \item Optimize multiple data sources (images) in parallel: requires some kind of
        "normalization" to ensure that the dimensions, pixels etc. are the same such that parameters
        are comparable; also requires identical experimental setup
        \item Compare different species with various modifications
        \item Modify model futher; asymmetric forces etc.
    \end{itemize}
\end{itemize}
